### 2021-12-30 cleave.tex
adding acronyms

% A system for the benchmarking of Networked Control Systems needs to be able to 
% \todo[inline]{Explain what it needs}
Existing platforms for NCS benchmarking take one of two approaches.
The first is a fully simulated approach, in which the plant, network and controller reside in a completely simulated environment.
This allows for unparalleled flexibility, as parts of the system can be swapped out or modified without greater difficulty.
However, this comes at the cost of realism, as these models are always approximations of reality; and time, as these simulations are often very computationally expensive.

The alternative is an approach using a testbed comprised of a \emph{physical} plant that interacts with a \emph{real} network and controller.
This of course allows for great realism, but provides very little flexibility in terms of the components of the system, limiting the approach to whatever plant, network and controller are available.

CLEAVE tries to mitigate the shortcomings of these approaches by walking the line between them.
We employ a third strategy based on having a real-time emulated representation of a control system interacting with a real network.
This allows for great flexibility when it comes to the components of the control system, as these are as easily switched out as in the fully simulated approach, while maintaining the realism of arguably the most complex and limiting component of an NCS, namely the network itself.

In the following we will explain the approach taken in CLEAVE by walking the reader through the steps necessary to deploy an arbitrary NCS emulation on top of the framework.
An overview of the structure of an NCS emulation on CLEAVE can be seen in \cref{fig:cleave:ncs:struct}.

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{images/CLEAVE_NCS_structure.png}
    \caption{
        Structure of an emulated NCS on top of CLEAVE.
        The State object implements the discrete-time evolution of the Plant.
        For this purpose, it holds two sets of special variables; Actuated Variables and Sensed Variables.
        Actuated Variables are updated from the values obtained from the Actuator objects at the beginning of each time step.
        These are used to perform a time step update in the State, and update the values of the Sensed Variables.
        The values of the Sensed Variables are then, at the end of each time step, sampled and passed on to the Sensor objects, which in turn process them (for instance, to add noise) and send the processed values to the Controller.
        The Controller uses these values to calculate the new actuation commands and sends these to the Actuators.
        Finally, the Actuators process the actuation commands and hold the new values for the Actuated Variables until they are read at the next time step.
    }\label{fig:cleave:ncs:struct}
\end{figure*}

@@

The first step in developing an NCS emulation on top of CLEAVE is the definition of a Plant which represents the physical system to be controlled.

@@

After the Plant has been defined, users need to implement a Controller for it.
This is once again done by extending an abstract base class, \texttt{Controller}, provided by CLEAVE.
This class defines a single abstract method, \texttt{Controller.process()} which is called by the framework whenever samples are provided by the Plant.
When invoked, it is passed a mapping of property names to sampled values.
The framework also expects implementations of this method to return yet another mapping, this time of actuated property names to target values.
Users are otherwise free to implement any kind of logic or process within extending classes.

>>>>

% A system for the benchmarking of Networked Control Systems needs to be able to 
% \todo[inline]{Explain what it needs}
Existing platforms for \acp{NCS} benchmarking take one of two approaches.
The first is a fully simulated approach, in which the plant, network and controller reside in a completely simulated environment.
This allows for unparalleled flexibility, as parts of the system can be swapped out or modified without greater difficulty.
However, this comes at the cost of realism, as these models are always approximations of reality; and time, as these simulations are often very computationally expensive.

The alternative is an approach using a testbed comprised of a \emph{physical} plant that interacts with a \emph{real} network and controller.
This of course allows for great realism, but provides very little flexibility in terms of the components of the system, limiting the approach to whatever plant, network, and controller are available.

Our approach, CLEAVE, tries to mitigate the shortcomings of these approaches by walking the line between them.
We employ a third strategy based on having a real-time emulated representation of a control system interacting with a real network.
This allows for great flexibility when it comes to the components of the control system, as these are as easily switched out as in the fully simulated approach, while maintaining the realism of arguably the most complex and limiting component of an \ac{NCS}, namely the network itself.

In the following we will explain the approach taken in CLEAVE by walking the reader through the steps necessary to deploy an arbitrary \ac{NCS} emulation on top of the framework.
An overview of the structure of such an emulation on CLEAVE can be seen in \cref{fig:cleave:ncs:struct}.

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{images/CLEAVE_NCS_structure.png}
    \caption{
        Structure of an emulated \ac{NCS} on top of CLEAVE.
        The State object implements the discrete-time evolution of the Plant.
        For this purpose, it holds two sets of special variables; Actuated Variables and Sensed Variables.
        Actuated Variables are updated from the values obtained from the Actuator objects at the beginning of each time step.
        These are used to perform a time step update in the State, and update the values of the Sensed Variables.
        The values of the Sensed Variables are then, at the end of each time step, sampled and passed on to the Sensor objects, which in turn process them (for instance, to add noise) and send the processed values to the Controller.
        The Controller uses these values to calculate the new actuation commands and sends these to the Actuators.
        Finally, the Actuators process the actuation commands and hold the new values for the Actuated Variables until they are read at the next time step.
    }\label{fig:cleave:ncs:struct}
\end{figure*}

@@

The first step in developing an \ac{NCS} emulation on top of CLEAVE is the definition of a Plant which represents the physical system to be controlled.

@@

After the Plant has been defined, users need to implement a Controller for it.
This is once again done by extending an abstract base class, \texttt{Controller}, provided by CLEAVE.\@
This class defines a single abstract method, \texttt{Controller.process()} which is called by the framework whenever samples are provided by the Plant.
When invoked, it is passed a mapping of property names to sampled values.
The framework also expects implementations of this method to return yet another mapping, this time of actuated property names to target values.
Users are otherwise free to implement any kind of logic or process within extending classes.
